The error in Bayesian phylogenetic reconstruction when speciation co-occurs

### 2018-12-04 article.tex
Move hypothesis to start of appendix to not seperate symbols and parameter values
Add MBD symbols lambda, mu, nu, q

\item To investigate the effect of $s$ on $e$, we simulate phylogenies
for different values of $s$ spread equally from zero (no multiple-birth
event, thus a BD model) to one (species are created only from multiple-birth
events) and three intermediate values of 0.25, 0.5 and 0.75. Aggregating all
components of $s$, we show the effect of $s$ on $e$ in figure 1.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}
  \centering 
  \begin{tabular}{r l}
    \hline
                          & Description\\
    \hline
    \hline
    $e$                   & Inference error \\
    $n_{\mathbb{M}}$      & Number of extant taxa created by a multiple-birth event \\
    $n_{\mathbb{B}}$      & Number of extant taxa created by a single-birth event \\
    $N_{\mathbb{M}}$      & Number of extinct and extant taxa created by a multiple-birth event \\
    $N_{\mathbb{B}}$      & Number of extinct and extant taxa created by a single-birth event \\
    $s$                   & Extent/strength of the multiple birth process \\
    $L_c$                 & MCMC chain length \\
    $L_{sc}$              & MCMC sub-chain length \\
    $\epsilon$            & relative error tolerance in marginal likelihood estimation \\
    \hline
  \end{tabular}
  \caption{
    Overview of the symbols. 
  }
  \label{table:symbols}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}
  \centering 
  \begin{tabular}{r l}
    \hline
                          & Value(s) \\
    \hline
    \hline
    $s$                   & 0.0, 0.25, 0.5, 0.75, 1.0 \\
    $L_c$                 & $10^6$ \\
    $L_{sc}$              & $10^4$ \\
    $\epsilon$            & $10^{-13}$ \\
    \hline
  \end{tabular}
  \caption{
    Overview of the simulation parameters. 
  }
  \label{table:parameters}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

\item To investigate the effect of $s$ on $e$, we simulate phylogenies
for different values of $s$ spread equally from zero (no multiple-birth
event, thus a BD model) to one (species are created only from multiple-birth
events) and three intermediate values of 0.25, 0.5 and 0.75. Aggregating all
components of $s$, we show the effect of $s$ on $e$ in figure \ref{fig:1}.

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}
  \centering 
  \begin{tabular}{r l}
    \hline
                          & Description\\
    \hline
    \hline
    $\lambda$             & Speciation rate from default single-birth process \\
    $\mu$                 & Extinction rate \\
    $\nu$                 & Multiple-birth event trigger rate \\
    $q$                   & Proportion of taxa that speciate during a multiple-birth event \\
    $e$                   & Inference error \\
    $n_{\mathbb{M}}$      & Number of extant taxa created by a multiple-birth event \\
    $n_{\mathbb{B}}$      & Number of extant taxa created by a single-birth event \\
    $N_{\mathbb{M}}$      & Number of extinct and extant taxa created by a multiple-birth event \\
    $N_{\mathbb{B}}$      & Number of extinct and extant taxa created by a single-birth event \\
    $s$                   & Extent/strength of the multiple birth process \\
    $L_c$                 & MCMC chain length \\
    $L_{sc}$              & MCMC sub-chain length \\
    $\epsilon$            & relative error tolerance in marginal likelihood estimation \\
    \hline
  \end{tabular}
  \caption{
    Overview of the symbols. 
  }
  \label{table:symbols}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}
  \centering 
  \begin{tabular}{r l}
    \hline
                          & Value(s) \\
    \hline
    \hline
    $s$                   & 0.0, 0.25, 0.5, 0.75, 1.0 \\
    $\mu$                 & 0.0, 0.1, 0.2 [TODO: can be more extreme] \\
    $L_c$                 & $10^6$ \\
    $L_{sc}$              & $10^4$ \\
    $\epsilon$            & $10^{-13}$ \\
    \hline
  \end{tabular}
  \caption{
    Overview of the simulation parameters. 
  }
  \label{table:parameters}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
